Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems

### 2025-03-28 paper/appendix.Rmd
Begins to take final Colin's comments

---
title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
subtitle: "Alain Danet (a,b), Loubna El Madouri (a,c), Andrew P. Beckerman (b),
Maud Mouchet (a), Colin Fontaine (a) and Elisa Thébault (d)"
date: Supplementary Material
output:
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
    toc: false
fontsize: 10pt
header-includes:
   - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
   - \usepackage{float}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand{\arraystretch}{1}
geometry: margin=2cm
bibliography: references.bib
number_sections: false
csl: pnas.csl
---

@@

# Comparison of analysis in space and time

We further assessed the consistency of the reported associations among temporal
trends by implementing two additional analyses. We first tested if the
associations among the temporal trends within sites was holding across sites,
i.e. using spatial variations in food web structure rather than temporal changes
over time (space-for-time hypothesis). Second, we performed theoretical
simulations with a bioenergetic food web model to cross-reference our site and
species specific empirical data on riverine fish with a more generalized
representation of food web dynamics known to represent accurate relationships
among our focal variables [@brose_allometric_2006; @eschenbrenner_diversity_2023;
@danet_response_2024]. With those additional empirical and theoretical data, we
assessed additional SEM models with the same structure as in Section 4.2.

# Disantengling functional and redundant links

@@

@@

```{r}
tps10_cap <- paste0("Distribution of temporal trends per decade of the food-web
  structure by site estimated from the Bayesian models using Best Linear
  Unbiaised Prediction (BLUP). Species richness and biomass temporal trends are
  reported in percentage change per decade. Dashed red line and solid black line
  respectively indicate 0 and median change.")

@@

```{r}
rand_sim_cap <- paste0(
  "Simulations of (b) nodes extinctions in the metaweb according to three
  scenarios: random extinction sequence (grey dots), extinction sequence by
  decreasing order of trophic level, extinction sequence by increasing order of
  trophic level. The black line represents the average prediction of a GAM
  linear model for the 50 random extinction sequences."
)
```

```{r ext, fig.cap=rand_sim_cap}
tar_load(figSext)
knitr::include_graphics(figSext[[1]])
```

>>>>

---
title: "Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems"
subtitle: "Alain Danet , Loubna El Madouri, Willem Bonnaffé, Andrew P. Beckerman,
Maud Mouchet, Colin Fontaine and Elisa Thébault"
date: Supplementary Material
output:
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
    toc: false
fontsize: 10pt
header-includes:
   - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
   - \usepackage{float}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand{\arraystretch}{1}
geometry: margin=2cm
bibliography: references.bib
number_sections: false
csl: pnas.csl
---

@@

# Disentangling functional and redundant trophic pathways

@@

## References {-}

<div id="refs"></div>

# Supplementary results: comparison of analysis in space and time

We further assessed the consistency of the reported associations among temporal
trends by implementing two additional analyses. We first tested if the
associations among the temporal trends within sites was holding across sites,
i.e. using spatial variations in food web structure rather than temporal changes
over time (space-for-time hypothesis). Second, we performed theoretical
simulations with a bioenergetic food web model to cross-reference our site and
species specific empirical data on riverine fish with a more generalized
representation of food web dynamics known to represent accurate relationships
among our focal variables. With those additional empirical and theoretical data, we
assessed additional SEM models with the same structure as in Section 4.2 (see
main text, Fig. 2a).

@@

```{r}
tps10_cap <- paste0("Distribution of temporal trends per decade of the food-web
  structure by site estimated from the Bayesian models using Best Linear
  Unbiased Prediction (BLUP). Species richness and biomass temporal trends are
  reported in percentage change per decade. Dashed red line and solid black line
  respectively indicate 0 and median change.")

@@

```{r}
rand_sim_cap <- paste0(
  "Simulations of trophic species extinctions in the metaweb according to three
  scenarios: random extinction sequence (grey dots), extinction sequence by
  decreasing order of trophic level, extinction sequence by increasing order of
  trophic level. The black line represents the average prediction of a GAM
  linear model for the 50 random extinction sequences. Please note that the
  results are qualitatively similar that when considering species (see Fig. 3b,
  main text) instead of trophic species."
)
```

```{r ext, fig.cap=rand_sim_cap, out.width = "100%"}
tar_load(figSext)
knitr::include_graphics(figSext[[1]])
```
